\documentclass[11pt,a4paper]{article}
\usepackage{multirow}
\usepackage{booktabs}
\title{Change cursor face of Linux Console}
\author{Sugizaki Yukimasa (Namiki Secondary School, Ibaraki Prefecture)}
\date{\today}

\begin{document}
\maketitle
\abstract{
In Linux console, shapes, colours and blinking can be changed.
This paper explains how to change and set as default.

\tableofcontents

\section{By using Escape squences} \label{sec:cursor-esc}
Define escape charactor as \texttt{ESC}.

The format is below. \\
\verb|ESC[?A;B;Cc|
(\texttt{A}, \texttt{B} and \texttt{C} are 8-bit decimal numbers.)

\subsection{Parameter \texttt{A}}
Parameter \texttt{A} changes cursor shapes and states.
Table\ref{tab:param-A-effects} shows effects of parameter \texttt{A}.
\begin{table}[htb]
\begin{center}
\begin{tabular}{|c|l|}
\toprule
number & effect \\
\hline\hline
0 & default \\
1 & underline \\
$\cdots$	\\
8 & full block \\
\hline
$number+16$ & apply the software cursor \\
\bottomrule
\end{tabular}
\label{tab:param-A-effects}
\caption{Effects of parameter \texttt{A}}
\end{center}
\end{table}
Cursor and characters colour can be changed by the parameter \texttt{A} and \texttt{B}
if the software cursor applied.

\subsection{Parameter \texttt{B}}
Parameter \texttt{B} changes the colour and brightness of cursor and charcters.
Table \ref{tab:param-B-bit-assignments} shows the bit assignments of parameter \texttt{B}.
\begin{table}[htb]
\begin{center}
\begin{tabular}{|c|l|l|}
\toprule
field\verb|#| & effect if 1 \\
\hline \hline
1 & \multirow{4}{*}{cursor} & bright \\
2 && red component \\
3 && green component \\
4 && blue component \\
\hline
5 & \multirow{4}{*}{characters} & bright \\
6 && red component(reversed) \\
7 && green component(reversed) \\
8 && blue component(reversed) \\
\bottomrule
\end{tabular}
\label{tab:param-B-bit-assignments}
\caption{Bit assignments of parameter \texttt{B}}
\end{center}
\end{table}

\subsection{Parameter \texttt{C}}
Effect of Parameter \texttt{C} is described as equation \ref{eqn:param-C-effect}.
\begin{equation}
	B=B \bigoplus C
\label{eqn:param-C-effect}
\end{equation}


\section{Set cursor shape as default in kernel command line}
We use escape-squence-formed cursor shape settings(parameter \texttt{A}, \texttt{B} and \texttt{C} in section \ref{sec:cursor-esc}) in kernel command line.
The form is below. \\
\par
\verb|vt.cur_default=0xCCBBAA| \\
Note that CC, BB and AA are hexadecimal number.
\end{document}
